In this, project I have used Node.js, Express.js framework, Mongoose for MongoDB and the middleware such as crypto, autocomplete and connect.\\
\\
Nowadays people have certain degree of waste in shopping. Sometimes they are impulsive to buy items when the shop has discounts or privileges.\\
And there also have a different situation like me an international student who need study and live in a foreign country for a few years, and in the end of studying when they need back to home country a lot of living products must cannot take to home. So, I built a shopping website to help people who need to sale second-hand item or buy those use low-price. And this website I used Node.js and MongoDB to realize all functions I need. Node.js is a new software development platform, it is not only a separate language, but also with Python, Ruby, as not only a language but also internet. Node.js the JavaScript from your browser ported to the common server. So that JavaScript can be achieved such as file systems, operating systems, network communications and other functions. Node running on Chrome V8 engine, asynchronous I / O architecture and design and single-threaded event-driven model, and built-in HTTP server it is mainly used to build high-performance, high-concurrency, high scalability of the server \cite{1}. Develop a Web application, the most important is the database using, MySQL, PHP was best partner in the past, and now there is MongoDB and Node.JS make the best combination. MongoDB have some special features that is a new NOSQL Data Base and Simple use, free, open source and ready to download \cite{2}.  \\
Based on those points, this website I use a flexible and small frame named Express.js that can make Node.js easy and improve application running efficiency in the same time. Express.js is a frame in Node.js that be developed to solve website problem and based on the existing framework for analyzing different platforms to extract feature points of the frame. These include routing and forwarding function point mapping, property injection, Cookie achieve , Session realization. \\
\\
\\
Key Point: Shopping, Second-Hand Product, Node.js, MongoDB, Express.js.\\