After nearly two months of unremitting efforts, finally finished my graduation website Design. The Application's title is "Second-Hand shopping website".\\
\\
When i first time know final year design is no limits on type, im so excited because i can do the Second-hand shopping website that raised this idea when i arrive Ireland. At begin of project I went to the library, bookstore to check a lot of information on network database about the "online shopping system".\\
\\
This Project was made by the Nodejs, database was built by MongoDB. To that end, I took three weeks to get used to write Nodejs page and the MongoDB database using the method. Through the above preparatory work, made my follow-up developed smoothly, will not affect the progress of some difficulty, guarantee paper finish at time.\\
\\
When i begin designing this system, primarily defining the database and initialize the data. This technical work is not strong, simply enter all data. When database design is complete, and start entering the Web page programming, is the most time consuming job. In this process, the problems encountered are mostly grammatical problems, also had a few appearances database connection. Such as database storage path is changed while in use, leads to cannot access the data via a Web page, only to specify a path statement in your Web page code make the appropriate modifications, to make it accessible.\\
\\
In the system design process, I got help from classmates, they make my schedule did not stagnate, let me save a lot of detours. It also made me see the truth, no one can execute, do it all without missing, something beyond the reach of your place. Communication is the best way to solve these problems. Through this graduation thesis design, not only improved my ability to solve problems, is the exercise of my own programming ability, I provided valuable experience for future development.\\
\\
Due to time constraints and the lack of practical experience, and performed by the graduation system where many have yet to be improved.\\
\\
Overall, graduated design although end has, by prepared of software although also has many of vulnerability, believes in teacher's eyes this project also has many childish and insufficient  place, but this graduated design does up to has is big of effect, it is a bog check by learn to of knowledge in this year, also let me have new awareness to future career. I think the results of the design is not important, summed up the most important thing is the experience and knowledge they acquired from the production process.