\section{How i did my project}
\subsection{Developing Method}
I used Node.js, Express.js and MongoDB to develop shopping website. Firstly I make a requirements analysis and then I use Rapid Prototype Model \cite{17} create a template only have front-end.\\
\\
\subsection{Discuss requirements of Website}
A good online shopping system, not only include an optimized back-end but also need a beautiful front-end, this system is consist by four part: 
Firs: the customers browsing module;\\
Second: application service module; \\
Third: the back-end database module; \\
Fourth: is a most important one, and back-end systems client management module.\\
At the front desk of the modules contained in the registration, login, logout processing functions, and function of these three modules are included in the query. Modules in the background, only the administrator has the authority to login, the administrator can add product information, customer, you can edit details of the commodity and so on a series of functions.\\
I start make front-end (website framework) and thinking the necessary functions will used in my project. I create login, logout, account.
And display some items on this page. Then start do the back-end.\\
\\
\section{Development tools} 
\subsection{The hardware environment} 
Laptop configuration: CPU: I5-5200U 2.2GHz; \\
\\
RAM: 8 GB; Memory: 512GB\\
\\
Operation System: Microsoft Windows 10 \\
\\
\subsection{Software Environment}
Developing tool : KOMODO IDE 9 \\
\\
Browser: Firefox, chrome\\
\\
Development Environment: Node.js\\
\\
Database: MongoDB\\
\\
\subsection{Komodo Edit \cite{6}}
\\
Download address: https://github.com/Komodo/KomodoEdit\\ 
\\
Komodo Edit is a free text editor for dynamic programming languages. It was introduced in January 2007 to complement Active State's commercial Komodo IDE. As of version 4.3, Komodo Edit is built atop the Open Komodo project. Many of Komodo's features are derived from an embedded Python interpreter.\\
\\
\section{Platform Brief }
\subsection{GitHub profile \cite{8}}
\\
GitHub is a shared hosting services that use the Git to share system projects. It were made by the GitHub Company’s (called Logical Awesome) developers Chris Wanstrath, and PJ Hyatt, and Tom Preston-Werner write by Ruby on Rails. GitHub also offers paid accounts and free accounts for open source projects. According to the Git user survey, GitHub is the most popular of the Git access site. \\
GitHub Personal information library, and the Wiki page through a git repository you can edit these pages. As a distributed version control system, Git does not have a main library in concept, each copy out of warehouse can be used independently, and any difference between these warehouses can be merged together.\\ 
GitHub can host a variety of git, and provides a unified Web interface. But provide different service with others Code manage website such as Source Forge and Google Code,GitHub is unique to branch a project management is very simple, has a high degree of interoperability. If you want to contribute code for a project is an easy task: first on the project site of the "fork" button, then check out the code and to add modifications to separate code libraries, and finally through the built-in "pull request" mechanism to apply to the project director code.\\ 
\\