\section{Advantages}
This is a Nodejs project which have better performance than JSP, it can run and get data form back-end faster. And in website application i design many part to ensure protect consumers' information such as encrypt password, authorised database and used session. \\
\section{Limitation}
Due to the short development time, website design is not good enough, and there also have a lot of flaws in code. But I think this website will better with the Node.js platform developing and continue maintains.\\
Code inefficiency.\\
Firstly, manage and control node.js asynchronous processing mechanism not skilled enough cause short development time. Typing a lot of code that inefficient. If the requested data objects in the data object has too many levels may lead to response time too long to respond to interrupts
\\
Function realization not rigorous.\\
Certain features in the website are not completed finished because the time problem. When consumer frequent refresh page or visit this website maybe will result in crashes. For example  Session data. Not strictly limit each user can hold Session data size. If there is a storing data in session , because the Session data has been stored in memory, and so easily because the data is too large causing memory overflow problem.
\\
Log function is missing.\\
Node.js's platform log output to the console can print certain information. In the early time of website design do not have a completed log processing module, just printed on the console. With the application of the project, once the error occurred during the operation, just displayed in the console does not work once the console closes these error messages follow disappear. The server-end requires a logging module, framework error need be logged in the log file, help to exclude errors. Currently this feature is not exist yet.\\
\\
Didn't bind a domain to website, it's a biggest problem.\\
\\
The content above is talking about the limitations of website, and following introduction is describe future development of the project and functions issues;
\\
\section{Future Development and Optimization}
Optimize my code.\\
Optimize some code for functions, using a high efficient algorithms to do some data processing.\\
\\
Implementing logging.\\
Finish logging module to store Log error messages to a local memory , you can configure the output format and the output according to the information level.\\
\\
Bind a domain to website, it can provide a better experience to consumer and also can test help people to buy low-price product or dispose furniture or electric applications they don't need.\\
\\ 
The website source code will host on GitHub so that I can improve and modify, make it more prefect and efficient. Open over the network can be modified together looking for people who possess the same interest so people know and are willing to try. This is the ultimate purpose of this framework.\\
\\
This chapter introduced the framework of the specific deficiencies and inadequate quarters do revise and perfect plan. And illustrate the development of the framework for the final desired result.
